Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2015-01-15 paper/sheaf_lics.tex
section 4 completed, with remarks

As recall in Section~\ref{sec:lawv-tiern-sheaf}, in topos theory,
sheaves are elements that can not distinguish between objects and
their dense sub-objects. Here, we need to distinguish between
dense $(-1)$-subobjects, that will be used in the definition of
sheaves, and dense $n$-subobjects, that will be used in the definition
of separated types.

\begin{defi}
  For any $A, E:\Type$ and $F:\Type_{n+1}$, we define~:
  \begin{itemize}
  \item if $m : A \hookrightarrow E$ is a monomorphism, we define 
    %
    $$
    M_E^\chi : (E \to F) \to (A \to F)
    $$
    %
    is the map sending an
    arrow $f~:~E\to F$ to $\restriction f A$ the restriction of $f$ to $A$.
  \item if $A \to E$ with $n$-truncated homotopy fibers, $\Phi_E^\chi$ is the
    map sending $f~:~E \to f$ to $\restriction f A$.
  \end{itemize}
\end{defi}

\begin{defi}[Separated Type]
  A type $F$ in $\Type_{n+1}$ is {\em separated} if for any type $E$, and
  all dense subobject of $E$ classified by $\chi~:~E \to \Type_n$,
  $\Phi_E^\chi$ is a monomorphism. In other words, the dotted arrow,
  if exists, is unique.

  $$\xymatrix{
    \sum_{e:E} (\chi~ e) \ar[r]^f \ar[d]_{\pi_1} & F \\
    E \ar@{-->}[ru]_{!}&
  }$$
\end{defi}

\begin{defi}[Sheaves]
  A type $F$ of $\Type_{n+1}$ is a {\em $(n+1)$-sheaf} if it is
  separated, and for any type $E$ and all dense subobject of $E$
  classified by $\chi~:~E \to \Type_{-1}$, $M_E^\chi$ is an
  equivalence. In other words, the dotted arrow exists and is unique.

  $$\xymatrix{
    \sum_{e:E} (\chi~ e) \ar[r]^f \ar[d]_{\pi_1} & F \\
    E \ar@{-->}[ru]_{\exists !}&
  }$$
\end{defi}

Note that these definitions are almost the same as the ones
in~\cite{maclanemoerdijk}. The main difference is that {\em separated}
is defined for $n$-subobjects,
while {\em sheaf} only for $-1$-subobject.

>>>>

As recall in Section~\ref{sec:lawv-tiern-sheaf}, in topos theory,
sheaves are elements that can not distinguish between objects and
their dense sub-objects.

\begin{defi}
  For any type $A$ and $E$, $\iota : A -> E$ and $F:\Type_{n+1}$, we define
    $$
    \Phi_E^\iota : (E \to F) \to (A \to F) 
    $$
    %
    as the map sending an
    arrow $f:E\to F$ to its restriction the restriction of $f \circ m$.
  % \item if $A \to E$ with $n$-truncated homotopy fibers, $\Phi_E^\chi$ is the
  %   map sending $f~:~E \to f$ to $\restriction f A$.
  % \end{itemize}
\end{defi}

Here, we need to distinguish between
dense $(-1)$-subobjects, that will be used in the definition of
sheaves, and dense $n$-subobjects, that will be used in the definition
of separated types.

\begin{defi}[Separated Type]
  A type $F$ in $\Type_{n+1}$ is {\em separated} if for any type $E$, and
  all dense $n$-subobject of $\iota : A \to E$,
  $\Phi_E^\iota$ is a monomorphism. In other words, the dotted arrow,
  if exists, is unique.

  $$\xymatrix{
    A \ar[r]^f \ar[d]_{\iota} & F \\
    E \ar@{-->}[ru]_{!}&
  }$$
\end{defi}

\begin{defi}[Sheaves]
  A type $F$ of $\Type_{n+1}$ is a {\em $(n+1)$-sheaf} if it is
  separated, and for any type $E$ and all dense $(-1)$-subobject of
  $\iota : A \to E$, $\Phi_E^\iota$ is an
  equivalence. In other words, the dotted arrow exists and is unique.

  $$\xymatrix{
    A \ar[r]^f \ar[d]_{\iota} & F \\
    E \ar@{-->}[ru]_{\exists !}&
  }$$
\end{defi}

Note that these definitions are almost the same as the ones
in~\cite{maclanemoerdijk}. The main difference is that {separated}
is defined for $n$-subobjects, while {sheaf} only for
$(-1)$-subobjects

\nt{Il faut introduire c'est propriété, $\Type_n^\modal$ is a sheaf
  est très importante en particulier. Il faut qu'on comprenne d'où ça
  vient et que tu fasses un preuve, même un peu idalisée}
